Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-09-09 snapshot_system/fast14_evaluation.tex
updated dedup efficiency
update evaluation

{\bf Memory and disk bandwidth usage with multi-VM processing}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each node. 
Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of backing up multiple VMs 
at the same time on each physical machine. 
[ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
the cloud infrastructure services and are shared among many applications.]
We see our hybrid deduplication scheme only occupies a small amount of system resources. 
The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
memory during duplicate detection.

@@

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
snapshot space per VM caused  by approximate deletions.
The slot line is the predicted leakage using Formula~\ref{eq:leak} from Section~\ref{sect:delete}
while the dashed line is the actual leakage measured during the experiment.
[OTHER PARAMETERS USED]
After 9 snapshot deletions, the actual leakage reaches 0.01\% and this means that
there is only 1MB space leaked for every 10GB of stored data.

>>>>

{\bf Memory and disk bandwidth usage with multi-VM processing}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each node. 
Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of backing up multiple VMs 
at the same time on each physical machine. 
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
We see our hybrid deduplication scheme only occupies a small amount of system resources. 
The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
memory during duplicate detection.

@@

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The slot line is the predicted leakage using Formula~\ref{eq:leak} from Section~\ref{sect:delete}
while the dashed line is the actual leakage measured during the experiment.
% [OTHER PARAMETERS USED]
After 9 snapshot deletions, the actual leakage reaches 0.01\% and this means that
there is only 1MB space leaked for every 10GB of stored data.
